### 2017-05-19 manuscript/usses_water_ms.Rmd
adds rank clocks
trivia

\Large{\textbf{Ecosystem and community resistance to five years of drought and deluge in a sagebrush tteppe}}

@@

\normalsize{Andrew T. Tredennick\textsuperscript{1}, Andrew R. Kleinhesselink\textsuperscript{2}, and Peter B. Adler\textsuperscript{1}}

@@

\textit{\small{\textsuperscript{1}Department of Wildland Resources and the Ecology Center, Utah State University, Logan, Utah 84322}}
\textit{\small{\textsuperscript{2}Department of Ecology and Evolutionary Biology, University of California, Los Angeles, Los Angeles, California xxxxx}}

@@

>>>>

\Large{\textbf{Ecosystem and community resistance to five years of drought and deluge in a sagebrush steppe}}

@@

\normalsize{Andrew T. Tredennick\textsuperscript{1}, Andrew R. Kleinhesselink\textsuperscript{2}, Bret Taylor\textsuperscript{3}, and Peter B. Adler\textsuperscript{1}}

@@

\textit{\small{\textsuperscript{1}Department of Wildland Resources and the Ecology Center, Utah State University, Logan, Utah 84322}} \\
\textit{\small{\textsuperscript{2}Department of Ecology and Evolutionary Biology, University of California, Los Angeles, Los Angeles, California xxxxx}} \\
\textit{\small{\textsuperscript{3}U.S. Sheep Experiment Station, Range Sheep Production Efficiency Research Unit, USDA-ARS, Dubois, Idaho 83423}}

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[width=5in]{../figures/rank_clocks_cover.png}
  \caption{Rank clocks for cover by treatment. (A) All species. (B) Dominant species.}
\end{figure}
